Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-04 dropping.tex
Edits based on Ed's comments.

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as the check
for line 4 in Figure~\ref{fig:dropping.example_full}) can only cause
false negatives and will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false
positives is to associate a 1-bit flag with each metadata in order to mark these
metadata as valid or
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalid flags with metadata. Suppose that the monitoring for
line 1 is dropped in order to meet the overhead target. When a monitoring event is dropped, metadata that would have
been updated is marked as invalid. In this case, instead of the normal
operation of marking {\tt rf\_invalid[1]} as {\tt false}, it is instead
marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalid flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was in bounds.

@@

\begin{enumerate}
  \item Propagate invalid flags, following the dataflow of metadata.
  \item Filter out monitoring operations based on invalid flags.
\end{enumerate}

@@

Thus, the hardware acts effectively as a dataflow tracking engine in order to
track a 1-bit invalid flag per metadata. Figure~\ref{fig:dropping.dataflow} shows a detailed block
diagram of this hardware module. The dataflow engine uses two address
calculation units to read in up two invalid flags. These source invalid flags
are used to decide whether a monitoring event should filtered. A third address
calculation unit is used to optionally specify a target to propagate the
invalidation information. The module includes a register file to store invalid
flags corresponding to register file metadata. In addition, it uses a small
memory-backed cache to handle invalid flags corresponding to memory metadata.

@@

One way to reduce the number of monitoring events that must be handled by the
monitor is to filter out monitoring events that correspond to operating on null
metadata. Null metadata corresponds to events that
are not relevant to the monitor. For example, Hardbound
\cite{hardbound-asplos08} filters out operations on non-pointer (i.e., no base
and bounds metadata) instructions since it is not relevant to array bounds
checking. More recently, FADE \cite{fade-hpca14} has been proposed as a general
hardware module to perform this null metadata filtering for a variety of
monitoring schemes. Our architecture is able to support this null metadata
filtering with a small modification.

@@

The operations performed by null filtering are almost identical to the
operations needed for invalidation shown in
Figure~\ref{fig:dropping.example_invalid}. Instead of taking a logical OR of the
source invalid flags to determine whether monitoring can be skipped, null
metadata filtering takes a logical AND of the source null flags.
Thus, we can easily enable this null metadata filtering on our architecture by
extending the dataflow flags to be two bits wide. One bit is used to
keep track of invalidation information while the second bit is used to keep
track of null information. All flags are initialized to null and the filter
decision table is extended with the propagation and filtering decision rules
for null metadata filtering.
The result is a single hardware design that enables both partial
monitoring and null metadata filtering.

>>>>

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as the check
for line 4 in Figure~\ref{fig:dropping.example_full}) can only cause
false negatives and will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false
positives is to associate a 1-bit flag with each metadata in order to mark these
metadata as valid or
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalidation flags with metadata. Suppose that the monitoring for
line 1 is dropped in order to meet the overhead target. When a monitoring event is dropped, metadata that would have
been updated is marked as invalid. In this case, instead of the normal
operation of marking {\tt rf\_invalid[1]} as {\tt false}, it is instead
marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalidation flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was within bounds.

@@

\begin{enumerate}
  \item Propagate invalidation flags, following the dataflow of metadata.
  \item Filter out monitoring operations based on invalidation flags.
\end{enumerate}

@@

Thus, the hardware acts effectively as a dataflow tracking engine in order to
track a 1-bit invalidation flag per metadata. Figure~\ref{fig:dropping.dataflow} shows a detailed block
diagram of this hardware module. The dataflow engine uses two address
calculation units to read in up to two invalidation flags. These source invalidation flags
are used to decide whether a monitoring event should filtered. A third address
calculation unit is used to optionally specify a target to propagate the
invalidation information. The module includes a register file to store invalidation
flags corresponding to register file metadata. In addition, it uses a small
memory-backed cache to handle invalidation flags corresponding to memory metadata.

@@

One way to reduce the number of monitoring events that must be handled by the
monitor is to filter out monitoring events that correspond to operating on null
metadata. Null metadata correspond to events that
are not relevant to the monitor. For example, Hardbound
\cite{hardbound-asplos08} filters out operations on non-pointer (i.e., no base
and bounds metadata) instructions since it is not relevant to array bounds
checking. More recently, FADE \cite{fade-hpca14} has been proposed as a general
hardware module to perform this null metadata filtering for a variety of
monitoring schemes. Our architecture is able to support this null metadata
filtering with a small modification.

@@

The operations performed by null filtering are almost identical to the
operations needed for invalidation shown in
Figure~\ref{fig:dropping.example_invalid} except for a small change in the propagation policy. Instead of taking a logical OR of the
source invalidation flags to determine whether monitoring can be skipped, null
metadata filtering takes a logical AND of the source null flags.
Thus, we can easily enable this null metadata filtering on our architecture by
extending the dataflow flags to be two bits wide. One bit is used to
keep track of invalidation information while the second bit is used to keep
track of null information. All flags are initialized to null and the filter
decision table is extended with the propagation and filtering decision rules
for null metadata filtering.
The result is a single hardware design that enables both partial
monitoring and null metadata filtering.

### 2015-01-04 evaluation.tex
Update full monitoring overheads for FPGA and add 14x for BC.
Edits based on Ed's comments.

We implemented our dataflow-guided monitoring architecture by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. We implement the monitor as a software-based monitor
running on a parallel processor core, similar to LBA \cite{lba-asid06}.
We model the main and monitoring cores as
running at 2.5
GHz with 4-way set-associative 32 kB private L1 I/D caches and a shared 8-way 2 MB L2
cache. This setup is similar to the Snapdragon 801 processor commonly found in
mobile systems. The dataflow engine uses a 1 kB cache for invalid and null flags.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. This may
not necessarily be true for actual errors/attacks and so the reported coverage
may not be the same as the probability of detecting actual errors/attacks.
However, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.7x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-2.0x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing 45\% coverage.

@@

From these results, we see that depending on the monitor and the program
behavior, source-only dropping can provide better coverage than unrestricted
dropping with the same overhead. Overall, unrestricted dropping is better at
meeting an overhead target.
Thus, for applications where staying within an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

Adding the dataflow engine in order to enable filtering and partial monitoring adds
overheads in terms of area and power. We use McPat \cite{mcpat-micro09} to get
a first-order estimate of these area and power overheads in a 40 nm technology
node. McPat estimates the main core area as 2.71 mm$^2$ and the peak power usage as
965 mW averaged across all benchmarks. The average runtime power usage was 385 
mW. These area and power numbers consist of the core and
L1 cache, but do not include L2 cache, memory controller, and other
peripherals. The power numbers include dynamic as well as static (leakage)
power. For the dataflow engine, we modeled the ALUs used for address
calculation, the dataflow flag register file and cache, the configuration
tables, and the filter decision table. These were modeled using the
corresponding memory and ALU objects in McPat. We
note that this is only a rough area and power estimate since components such as the
wires connecting these modules have not been modeled. However, this gives a
sense of the order-of-magnitude overheads involved with implementing our
approach.

>>>>

We implemented our dataflow-guided monitoring architecture by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. We implement the monitor as a software-based monitor
running on a parallel processor core, similar to LBA \cite{lba-asid06}.
We model the main and monitoring cores as
running at 2.5
GHz with 4-way set-associative 32 kB private L1 I/D caches and a shared 8-way 2 MB L2
cache. This setup is similar to the Snapdragon 801 processor commonly found in
mobile systems. The dataflow engine uses a 1 kB cache for invalidation and null flags.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds checking as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. This may
not necessarily be true for actual errors/attacks and so the reported coverage
may not be the same as the probability of detecting actual errors/attacks.
However, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.9x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-2.0x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing 45\% coverage.

@@

From these results, we see that depending on the monitor and the program
behavior, source-only dropping can provide better coverage than unrestricted
dropping with the same overhead. Unrestricted dropping is better at
meeting an overhead target.
Thus, for applications where staying within an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

Adding the dataflow engine in order to enable filtering and partial monitoring adds
overheads in terms of area and power consumption. We use McPat \cite{mcpat-micro09} to get
a first-order estimate of these area and power overheads in a 40 nm technology
node. McPat estimates the main core area as 2.71 mm$^2$ and the peak power usage as
965 mW averaged across all benchmarks. The average runtime power usage was 385 
mW. These area and power numbers consist of the core and
L1 cache, but do not include L2 cache, memory controller, and other
peripherals. The power numbers include dynamic as well as static (leakage)
power. For the dataflow engine, we modeled the ALUs used for address
calculation, the dataflow flag register file and cache, the configuration
tables, and the filter decision table. These were modeled using the
corresponding memory and ALU objects in McPat. We
note that this is only a rough area and power estimate since components such as the
wires connecting these modules have not been modeled. However, this gives a
sense of the order-of-magnitude overheads involved with implementing our
approach.

### 2015-01-04 introduction.tex
Edits based on Ed's comments.

% Parallel run-time useful
Run-time monitoring techniques have been shown to be useful for improving the
reliability, security, and debugging capabilities of computer systems. For
example, Hardbound is a hardware-assisted technique to detect out-of-bound
memory accesses, which can cause undesired behavior or create a security
vulnerability if uncaught \cite{hardbound-asplos08}.  Intel has
recently announced plans to support buffer overflow protection similar to
Hardbound in future architectures \cite{intel-mpx}. Similarly, run-time
monitoring can enable many other new security, reliability, and debugging
capabilities such as fine-grained memory protection \cite{mondrian-asplos02},
information flow tracking \cite{dift-asplos04, testudo-micro08}, hardware error
detection \cite{argus-micro07}, data-race detection \cite{radish-isca12,
cord-hpca06}, etc.

@@

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positive, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and the monitoring
coverage achieved.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine can enable null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show average slowdowns of 1.1-5.8x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for the monitors which showed over 2x
average overheads, slowdown could be cut to 1.5x while still achieving a
coverage of 14-85\% on average.

>>>>

% Parallel run-time useful
Run-time monitoring techniques have been shown to be useful for improving the
reliability, security, and debugging capabilities of computer systems. For
example, Hardbound is a hardware-assisted technique to detect out-of-bound
memory accesses \cite{hardbound-asplos08}.  Intel has
recently announced plans to support buffer overflow protection similar to
Hardbound in future architectures \cite{intel-mpx}. Similarly, run-time
monitoring can enable many other new security, reliability, and debugging
capabilities such as fine-grained memory protection \cite{mondrian-asplos02},
information flow tracking \cite{dift-asplos04, testudo-micro08}, hardware error
detection \cite{argus-micro07}, data-race detection \cite{radish-isca12,
cord-hpca06}, etc.

@@

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positives, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and increasing the monitoring
coverage.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine can enable null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show average slowdowns of 1.1-5.8x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for the monitors which showed over 2x
average overheads, slowdown could be cut down to 1.5x while still achieving a
coverage of 14-85\% on average.

### 2015-01-04 policies.tex
Various minor edits. Figure clean-up.
Edits based on Ed's comments.

Alternatively, we can specify a target overhead and estimate, at run-time, the
overheads of monitoring in order to decide whether dropping is needed.
The overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. In order to estimate overheads at run-time, we define \emph{slack} as the number of cycles of
monitoring overhead that can be incurred while staying within the budget
target. Slack is essentially the difference between the actual overhead seen
and the budget specified. Slack is generated as the main program runs and consumed as monitoring overheads occur.  For
example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles. 
In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over time.
In this slack-based policy, if the slack falls below zero (i.e., the overhead budget is exceeded), then
monitoring events should be dropped.

@@

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

In addition to deciding when dropping is required, trade-offs also exist in
deciding which events should be dropped.
The simplest policy is to drop any monitoring events when slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:policies.all_drop}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be dropped. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.
That is, by the time we decide to drop event {\tt E}, we have already 
updated metadata due to events {\tt C} and {\tt D} even though they are no longer needed.

@@

Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work and thus better coverage. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since each event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event will cause the final check to be
invalid.

>>>>

Alternatively, we can specify a target overhead and estimate, at run-time, the
overheads of monitoring in order to decide whether dropping is needed.
The overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. In order to estimate overheads at run-time, we define \emph{slack} as the number of cycles of
monitoring overhead that can be incurred while staying within the budget
target. Slack is essentially the difference between the actual overhead seen
and the budget specified. Slack is generated as the main program runs and consumed as monitoring overheads occur.  For
example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles. 
In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over time.
In this slack-based policy, if the slack falls below zero (i.e., the overhead budget is exceeded), then
monitoring events are dropped.

@@

\begin{figure}
  \begin{center}
  \subfloat[Unrestricted Dropping]{
    \includegraphics[width=\columnwidth]{figs/unrestricted_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[Source-only Dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

In addition to deciding when dropping is required, trade-offs also exist in
deciding which events should be dropped.
The simplest policy is to drop any monitoring events when slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:policies.all_drop}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be dropped. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.
That is, by the time we decide to drop event {\tt E}, we have already 
updated metadata for events {\tt C} and {\tt D} even though they are no longer needed.

@@

Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work and thus better coverage at a given overhead. However, because of the coarser-grained decision, it
may be more difficult to closely match overhead targets. We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since every event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event is likely to cause the final check to be
invalid by dropping at least one event in the chain.

### 2015-01-04 related.tex
Edits based on Ed's comments.

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overheads. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overheads but does not try
  to bound overheads, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, almost all previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

@@

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overheads
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overheads. QVM does prevents false positives
but does so be enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.

>>>>

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overheads. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overheads but does not try
  to bound overheads, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

@@

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overheads
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overheads. QVM does prevent false positives
but does so by enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.

### 2015-01-04 title.tex
Edits based on Ed's comments.

\title{
%Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
%Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering
Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering
}

\ifanonymized{\author{Anonymized}}
{\author{\IEEEauthorblockN{Daniel Lo, Tao Chen, Mohamed Ismail, and G. Edward Suh}
\IEEEauthorblockA{Cornell University\\
Ithaca, NY 14850, USA\\
\{dl575, tc466, mii5, gs272\}@cornell.edu}}
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, for monitoring techniques with average
overheads of 2-6x, the proposed architecture is able to reduce slowdowns to
1.5x while still achieving 14-85\% average coverage.

>>>>

\title{Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering}

\ifanonymized{\author{Anonymized}}
{\author{\IEEEauthorblockN{Daniel Lo, Tao Chen, Mohamed Ismail, and G. Edward Suh}
\IEEEauthorblockA{Cornell University\\
Ithaca, NY 14850, USA\\
\{dl575, tc466, mii5, gs272\}@cornell.edu}}
}
% Reduce space between title and authors
\IEEEspecialpapernotice{\vspace{-0.4in}}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overhead through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overhead.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overhead can be reduced significantly 
by trading off coverage. For example, for monitoring techniques with average
overheads of 2-6x, the proposed architecture is able to reduce overhead to
1.5x while still achieving 14-85\% average coverage.
